Automating the Ontological Argument

### 2015-12-22 Papers/InProgress/IJCAI/paper.tex
Types reinserted in QML_S5 -- without types Modal Collapse has a Countermodel! This is interesting for further studies.
references added (essence)

\section{Variants of the Ontological Argument}
Short history, Anselm, Leibniz, etc.
\subsection{G\"{o}del's Proof Script}
\subsection{Scott's Variant}
\subsection{Recent Variants}

@@

\section{Full Automation of Scott's Proof}
Within the modified logic S5 Scott's proof can be fully automated. The
intermediate argumentation steps as not needed anymore to support the
prover, see Fig.~\ref{ScottS5}).
\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/ScottS5.png}}
\caption{Full Automation of the Ontological Argument in S5} \label{ScottS5}
\end{figure}

@@

\subsection{Argument Reconstruction in Isabelle}
Present the argument informal and in Isabelle (see
Fig.~\ref{InconsistencyIsabelleK}). Easy to understand in 
in KB and KT, slightly harder in K.
\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/InconsistencyIsabelleK.png}}
\caption{Reconstruction of inconsistency in Isabelle/HOl..} \label{InconsistencyIsabelleK}
\end{figure}

>>>>

\section{Variants of the Ontological Argument}
Short history, Anselm, Leibniz, etc.
\subsection{G\"{o}del's Proof Script}
\subsection{Scott's Variant}
\subsection{Recent Variants}
Dozens of contributions were published in the last four decades which
present variants of G\"odel's/Scott's proofs. In many cases the
motivation has been to remedy the modal collapse. Other authors are
simply interested in a critical assessment. Particularly interesting
from the perspective of this paper is that many literature
contributions unfortunately work with or refer to G''odel's original
definition of essence
$$ todo $$
This original version avoids the conjunct added by Scott expressing
that essential properties of an individual should be possessed by the
individual. As we show in this paper using this notion of essence
leads to an inconsistent axiom system, which in a classical setting of
course deserves no further attention, since from an inconsistent
system everything can be concluded, including God's existence and
non-existence simultaneously. In other words, these literature
contributions discuss variants of the argument which from a classical
logical perspective do not deserve any further attention.

We give here a list of examples:
\begin{itemize}
\item Anderson and Getting's 1996, p. 168 \cite[p.168]{AndersonGettings1968}
  use essence without conjunct.
\item  Hazen 1998, p.365 \cite[p.365]{Hazen1998} states: ``G\"odel left this
  clause out in [11], but this appears to have been an oversight--it
  is included in related manuscripts''. There is not mentioning of an
  inconsistency though.
\item Look???, p. 514
\item Oppy 1996, p.226-227 \cite[p.226/227]{Oppy1996}, Oppy 2000, p. 364
  \cite[p.364]{Oppy200}, Oppy 2008, p. 1068 \cite[p.1068]{Oppy2008}:
  Oppy uses: ``A is an essence of x iff for every property B, x has B
  neces- sarily iff A entails B'' (this is from Anderson's
  emendation). Check is this leads to inconsistency as well. In this
  case we may write something like:

 Oppy presents an critical
  assessment in order to conclude that G\"odel's argument fails to
  convince. Oppy apparently does not see that he is assessing an
  inconsistent axiom system (and he in fact creates adaptations that
  suffer the same problems).
\item 
\end{itemize}

\footnote{Fuhrmann2005: Gödel vermerkt diese Konsequenz [dass aus der Definition unmittelbar folgt, daß alle wesentlichen
Eigenschaften notwendig äquivalent sind] in einer Fußnote zur Definition. Die Definition selbst aber läßt im Definiens das Konjunkt Xx aus. Ohne das Konjunkt folgt jedoch die Konsequenz nicht. Es ist deshalb naheliegend anzunehmen, daß Gödel die Definition so beabsichtigte, wie sie hier notiert ist und wie Gödel sie selbst in früheren Notizbucheintragungen formuliert hat.}

@@

\section{Full Automation of Scott's Proof}
Within the modified logic S5 Scott's proof can be fully automated. The
intermediate argumentation steps as not needed anymore to support the
prover, see Fig.~\ref{ScottS5}).
\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/ScottS5.png}}
\caption{Full Automation of the Ontological Argument in S5 } \label{ScottS5}
\end{figure}

@@

\subsection{Argument Reconstruction in Isabelle}
Present the argument informal and in Isabelle (see
Fig.~\ref{InconsistencyIsabelleK}). Easy to understand in 
in KB and KT, slightly harder in K.
\begin{figure}
%\centerline{\includegraphics[width=\columnwidth]{./Images/InconsistencyIsabelleK.png}}
\caption{Reconstruction of inconsistency in Isabelle/HOl..} \label{InconsistencyIsabelleK}
\end{figure}
